# Google Data Analytics Capstone - Bellabeat

This is an optional capstone project of Google Data Analytics Specialization on [Coursera](https://www.coursera.org/professional-certificates/google-data-analytics).

## Steps

1.  Ask
2.  Prepare
3.  Process
4.  Analyze
5.  Share
6.  Act

## Step 1: Ask

To begin with, I identify the business task of this project and key stakeholders who involved

### 1.1 Business Task

Analyze FitBit fitness tracker customer data trends to help influence Bellabeat marketing strategy.

### 1.2 Key Stakeholders

-   Urška Sršen: Bellabeat's cofounder and Chief Creative Officer
-   Sando Mur: Mathematician and Bellabeat's cofounder; key member of the Bellabeat executive team
-   Bellabeat marketing analytics team: A team of data analysts who guides Bellabeat's marketing strategy

## Step 2: Prepare

Next, I identify the data along its characteristics.

### Data Source

The data being used is stored on [Kaggle](https://www.kaggle.com/datasets/arashnic/fitbit) and contains 18 csv files.

### Data Selection

The data that is selected for this analysis is the dailyActivity_merged.csv file.

## Step 3: Process

In the Process step, I check data errors, transform the data, and clean the data to be analyzed.

#### Loading Packages

```{r}
library(tidyverse)
library(lubridate)
library(dplyr)
library(ggplot2)
library(tidyr)
```

#### Import data

```{r}
data <- read.csv("./data/dailyActivity_merged.csv")
```

### Display the imported data

```{r}
head(data)
```

```{r}
str(data)
```

### Explore data

```{r}
n_distinct(data$Id)
```
From the result above, it shows that there are 33 unique id

### Fix formatting
Here, I convert the ActivityDate to yyyy-mm-dd data type

```{r}
data$ActivityDate = as.Date(data$ActivityDate, format="%m/%d/%Y")
str(data$ActivityDate)
```

## Step 4: Analyze

### Summarize the data
```{r}
data %>%  
  select(Id,
         Calories) %>%
  summary()
```

```{r}
data %>%  
  select(TotalSteps,
         TotalDistance,
         TrackerDistance,
         LoggedActivitiesDistance) %>%
  summary()
```
```{r}
data %>%  
  select(VeryActiveDistance,
         ModeratelyActiveDistance,
         LightActiveDistance,
         SedentaryActiveDistance) %>%
  summary()
```
```{r}
data %>%  
  select(VeryActiveMinutes,
         FairlyActiveMinutes,
         LightlyActiveMinutes,
         SedentaryMinutes) %>%
  summary()
```

## Step 5: Share
In this step, I make several visualization of the data

### 